Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and Procedures

### 2014-01-24 rules/rules14.tex
Initial version (from 2012) of the 2014 rules

@@

\item QF\_UFLIA: uninterpreted functions and linear integer arithmetic (benchmarks may also be taken from  QF\_LIA). This division evaluates reasoning about integers.
\item QF\_UFLRA: uninterpreted functions and linear real arithmetic (benchmarks may also be taken from  QF\_LRA). This division evaluates reasoning about real numbers.

@@

The unsat-core track will be scored as follows. The score for each benchmark is a triple $\langle e,n,m\rangle$, with
$e$ a non-negative number of erroneous results,
$n$ the number of formula in the unsat core for the benchmark,
and $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
the timeout. 
The score for the benchmark is initialized with
$\langle0,0,0\rangle$ and then computed as follows.
\begin{itemize}
\item A correctly-reported unsat-core answer after
  $s$~seconds (counting from the beginning of this particular
  \akey{check-sat}) contributes $\langle0,n,s\rangle$ to the running
  score, where $n$ is the number of formula in the unsat core.
\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
  execution of the query, or a benchmark timeout, aborts the execution
  of the benchmark and assigns a score of $\langle0,N,T\rangle$ for the benchmark, where
  $N$ is the number of named asserted formula in the benchmark and $T$ is the timeout value.

\item The score for an incorrect answer to a \akey{check-sat} or \akey{get-unsat-core} command 
  will be $\langle1,N,T\rangle$, where
  $N$ is the number of named asserted formula in the benchmark and $T$ is the timeout value.
\end{itemize}

Scores are summed and ordered as for the main track, except that lower $n$ values are preferred, rather than higher values.

>>>>

In addition, the organizers reserve the right to include in the benchmark population benchmarks
from subsumed logics. For example, QF\_UFLIA may include some samples from QF\_LIA, and QF\_UFLRA may include some from QF\_LRA.
We will not use benchmarks from QF\_UF in other divisions.

@@

\item QF\_UFLIA: uninterpreted functions and linear integer arithmetic. This division evaluates reasoning about integers.
\item QF\_UFLRA: uninterpreted functions and linear real arithmetic. This division evaluates reasoning about real numbers.

@@

The unsat-core track will be scored as follows. The score for each benchmark is a triple $\langle e,n,m\rangle$, with
$e$ a non-negative number of erroneous results,
$n$ the reduction in number of formula in the unsat core for the benchmark,
and $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
the timeout. 
The score for the benchmark is initialized with
$\langle0,0,0\rangle$ and then computed as follows.
\begin{itemize}
\item A correctly-reported unsat-core answer after
  $s$~seconds (counting from the beginning of this particular
  \akey{check-sat}) contributes $\langle0,n,s\rangle$ to the running
  score, where $n$ is the reduction in number of formula in the unsat core (number of named formula in the benchmark minus
  the number reported as the unsat core).
\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
  execution of the query, or a benchmark timeout, aborts the execution
  of the benchmark and assigns a score of $\langle0,0,T\rangle$ for the benchmark, where
  $T$ is the timeout value.

\item The score for an incorrect answer to a \akey{check-sat} command 
  will be $\langle1,0,T\rangle$, where
  $T$ is the timeout value.
\end{itemize}

Scores are summed and ordered as for the main track.
